Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-25 size_differentiated_export.tex
Updates from Overleaf

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) has the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments, where the number of seeded particles would vary to account for the different spectral slopes. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.

@@

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle downward flux, using Lagrangian particle-tracking. Downward particle flux is expected to be a combination of their sinking velocity and the vertical advective currents affecting the particle along its pathway. The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution}d for both summer and winter cases. In the summer, the PDF of particle density versus depth remains relatively narrow through time, and is centered on a depth level that can be predicted using a simple 1D gravitational model (see shaded curves in Figure \ref{fig: particle_depth_distribution}). PDFs of particle density also vary little among particles classes with different sinking velocities, suggesting that downward fluxes of particles is greatly dominated by gravitational settling and is not subject to significant vertical ocean currents.

@@

In the winter, however, the PDF of particle density versus depth is wider, in agreement with the stronger vertical ocean currents occurring in the winter (see Figure \ref{fig: dynamics}). The deviation in the downward particle flux from the traditionally considered 1D gravitational model can be seen in Figure \ref{fig: particle_depth_distribution} (panels (a)-(c)). Slower-sinking particles deviate more than faster-sinking particles, exhibiting median depth anomalies up to 50 m. This is due to the fact that slower-sinking particles spend more time in the mixed layer, where most of the stronger vertical currents tend to occur (Figure \ref{fig: dynamics}). An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (where particles are shallower than expected) and negative (particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km). This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles and their associated .%, which is explicitly shown in Figure \ref{fig: biomass_export}.

A relative amount of biomass is associated to the particles using equation \ref{eq: biomassjungeslope}. The PDF of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}. Following the traditional paradigm derived from the simple 1D gravitational model, the downward flux of biomass in the summer is dominated by faster-sinking particle classes capable of carrying particulate material downwards more efficiently. The contribution of slower-sinking particles, however, critically depends on the slope of the size spectrum (see Figure \ref{fig: sinking_velocity_spectrum}). As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases. In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.1\% to 10\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$. While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles. This result can be explained by the fact that, in the summer, vertical velocities are weak and vertical biomass fluxes are therefore gravitationally-driven.

@@

In the winter, the PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day. For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes. Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass. When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux. In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux.

@@

The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class cumulatively exported 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively. However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are considered in the following section.

@@

 Both ocean dynamics at submeso-scales and the Junge slope were identified as key factors impacting the respective role played by different particle classes in driving downward biomass fluxes. Simple Lagrangian particles were used to isolate the effects of these two factors. In reality, however, sinking velocities of particulate matter varies in time as the particles slowly remineralize. A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation \ref{eq: sinking_velocity_remin}, to investigate the impact that remineralization processes have on our findings. The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over shorter timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes. While this paradigm holds for flatter Junge slope, where the biomass content is dominated by faster-sinking particles, it becomes inadequate at steeper slopes.

 Figure \ref{fig: biomass_export_remin} shows the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without remineralization processes. As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time \fixme{refer to Fig 9?}.

 During summertime and in the absence of remineralization, downward fluxes of biomass are dominated by faster-sinking particles, even for steeper Junge slope. This is due to the fact that the flux of biomass $\left<wB\right> = \left<w_sB\right> + \left<w_aB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content. This is characteristics of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes. Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize. This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where the PDFs of relative biomass per particle class are centered over lower vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}. As a result, the gravitationally-driven term $\left<w_sB\right>$ becomes small, and the downward flux of biomass is generally advectively-driven. The advectively-driven component of the biomass fluxes is uniform across particle classes, as it only depends on ocean currents. Thus, in a advectively-driven system where $\left<w_sB\right> << \left<w_aB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a). When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics. Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes.

@@

\subsection{Particle export}
\label{sec: discussion_particle}

Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer. This change in dynamics has a clear impact on the export flux of all sinking-velocity classes modeled in this experiment. Particle export within a sinking-velocity class is hastened and occur over longer timescales. In fact, particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics. This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC. However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported over longer timescales. This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export (Figure \ref{fig: particle_export}).

In the summer, the gravitationally-driven export mechanism efficiently exports faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles. In the winter, however, the export mechanisms is advectively-driven, which leads to a slightly weaker export flux of faster-sinking particles than in the summer due to resuspension, but a much larger export flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}). These two competing mechanisms raise the question as to which process is most efficient in exporting particulate material below the winter mixed layer.

%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}). Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics. Therefore, export flux is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales. %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})? Showing stronger, more localized downwelling, and broader and weaker upwelling?

>>>>

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) has the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments, where the number of seeded particles would vary to account for the different spectral slopes. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we define a normalized biomass unit for $\xi =3$ as $B_0=$ 1. The values taken by $B_0$ for other Junge slopes $\xi$ are computed under the condition that the total amount of biomass is kept constant (Figure \ref{fig: sinking_velocity_spectrum}b).

@@

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle downward flux, using Lagrangian particle-tracking. Domain-averaged, downward particle flux is expected to be a combination of the flux driving by gravitational sinking ($\left<w_sB\right>$), and by the vertical advective currents affecting the particle along its pathway ($\left<wB\right>$). The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution}d for both summer and winter cases. In the summer, the PDF of particle density versus depth remains relatively narrow through time, and is centered on a depth level that can be predicted using a simple 1D gravitational model (see shaded curves in Figure \ref{fig: particle_depth_distribution}). The spread in the particle density also vary little among particle classes with different sinking velocities, suggesting that downward fluxes of particles is greatly dominated by gravitational settling and is not subject to significant vertical ocean currents.

@@

In the winter, however, PDFs of particle density versus depth is wider, in agreement with the stronger vertical ocean currents occurring in the winter (see Figure \ref{fig: dynamics}). A top-view of the deviation in the downward particle flux from the traditionally considered 1D gravitational model can be seen in Figure \ref{fig: particle_depth_distribution} (panels (a)-(c)). Slower-sinking particles deviate more than faster-sinking particles, exhibiting median depth anomalies up to 50 m. This is due to the fact that slower-sinking particles spend more time in the mixed layer, where most of the stronger vertical currents tend to occur (Figure \ref{fig: dynamics}). An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (i.e., particles are shallower than expected) and negative (i.e., particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km). This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles.%, which is explicitly shown in Figure \ref{fig: biomass_export}.

A relative amount of biomass is associated to the particles using Equation \ref{eq: biomassjungeslope}. PDFs of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}. Following the traditional paradigm derived from the simple 1D gravitational model, the downward flux of biomass in the summer is dominated by faster-sinking particle classes capable of carrying particulate material downwards more efficiently. The contribution of slower-sinking particles, however, critically depends on the slope of the size spectrum (see Figure \ref{fig: sinking_velocity_spectrum}). As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases. In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.1\% to 10\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$. While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles. This result can be explained by the fact that, in the summer, vertical velocities are weak and vertical biomass fluxes are therefore gravitationally-driven ($\left<w_sB\right> > \left<wB\right>$).

@@

In the winter, PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day. For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes. Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass (Figure \ref{fig: biomass_export}b). When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux. In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux.

Our results show that both a steepening of the particle size spectra and the presence of submesoscale dynamics can enhance the contribution of slower-sinking particles to the downward biomass flux. While the former is simply due to an increase in particle density in slower-sinking particle classes, the latter is attributed to the larger vertical velocity generated by submesoscale instabilities. When both are combined, as expected in the wintertime, slower-sinking particles then become the leading contributor to the downward biomass transport. However, slower-sinking particles are generally expected to remineralize on timescales shorter than their export timescale, fueling the argument that the focus should be upon faster-sinking particle classes. The impacts of remineralization on export are thus considered in the following section to test the robustness of the findings.

@@

% The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class cumulatively exported 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively. However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are considered in the following section.

@@

 Both submesoscale dynamics and the Junge slope were identified as key factors impacting the respective role played by different particle classes in driving downward biomass fluxes. Simple Lagrangian particles were used to isolate the effects of these two factors. In reality, however, sinking velocities of particulate matter varies in time as the particles slowly remineralize. A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation \ref{eq: sinking_velocity_remin}, to investigate the impact that remineralization processes have on our findings. The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over short timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes. While this paradigm holds for flatter Junge slope, where the biomass content is dominated by faster-sinking particles, it becomes unfit at steeper slopes.

 Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without the remineralization scheme. \fixme{As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time} \fixme{refer to Fig 9?}.

 As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization. This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle. This is characteristic of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes. Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize. This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}. As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}). In a advectively-driven system where $\left<w_sB\right> < \left<w_B\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a). When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics (82\%; see Figure \ref{fig: biomass_export_remin}b). Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (87\%; see Figure \ref{fig: biomass_export_remin}d).

@@

\subsection{Downward Fluxes}
\label{sec: discussion_particle}

Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in downward particulate fluxes depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer. This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016}, characterizing the seasonal cycle of submesoscale dynamics. The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment. \fixme{export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC. Not sure I should talk about timescales anymore}

In the summer, the gravitationally-driven dynamics efficiently drives a downward flux dominated by faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles. In the winter, however, vertical fluxes tend to be advectively-driven, which leads to a slightly weaker downward flux of faster-sinking particles than in the summer due to resuspension, but a much larger flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}). These two seasonal mechanisms raise the question as to which process is most efficient in driving a downward flux of particulate material.

In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesocale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux. This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}). This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \citep{Kostadinov_2009, White_2015}. The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations describing the relationships between particle size, sinking velocity, and biomass content used in this study. Nevertheless, our results demonstrate that

%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}).

Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics. Therefore, export flux is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales. %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})? Showing stronger, more localized downwelling, and broader and weaker upwelling?
